Toward dynamic models of combat or lack thereof in animal mating

### 2015-12-22 ms.tex
Minor text change
changes to traits

\section{Figures}
Figure 1. Event Algorithm
Population state generates events, events are either:
\begin{enumerate}
    \item A new individual x has matured and entered the contest (based off of a trait(?))
    \item Discovery event wherin both a nest RR (repoductive resource) and an individual x are drawn from a pool, that nest is either:
\begin{enumerate}
    \item un-occupied: in which x takes ownership of RR.
    \item occupied by x' in which a constest occurs (see fig 2)
\end{enumerate}
\end{enumerate}
After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) < 0) then x is removed from the individual pool.

Figure 2. Contest Algorithm
for an occupier x' vs an invader x, there are 3 stages:
\begin{enumerate}
    \item Display 1
    \item Display 2
    \item Fight
\end{enumerate}
In the display phases the probability of escalation is dependant on the visible traits of x and x'
The rate of events increases as time t -> t1

Traits:
\begin{enumerate}
    \item Visible to opponent:
\begin{enumerate}
    \item Size
\end{enumerate}
    \item invisible to opponent:
\begin{enumerate}
    \item Energy levels
    \item Abandon Rate
    \item Aggression
    \item Encounter Rate
    \item Experience (?)
\end{enumerate}
\end{enumerate}

>>>>

\section{Figures}
\subsection {Figure 1. Event Algorithm}
Population state generates events, events are either:
\begin{enumerate}
    \item A new individual x has matured and entered the pool (based off of a trait(?))
    \item Discovery event wherin both a nest RR (repoductive resource) and an individual x are drawn from a pool, the metabolic costs of searching are deducted from the time differences between events, that nest is either:
\begin{enumerate}
    \item un-occupied: in which x takes ownership of RR.
    \item occupied by x' in which a constest occurs (see fig 2)
\end{enumerate}
\end{enumerate}
After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) less than 0) then x is removed from the individual pool.

\subsection{Figure 2. Contest Algorithm}
for an occupier x' vs an invader x, there are 3 stages:
\begin{enumerate}
    \item Display 1
    \item Display 2
    \item Fight
\end{enumerate}
In the display phases the probability of escalation is dependant on the visible traits of x and x'
The rate of events increases as time t approaches t1

Traits:
\begin{enumerate}
    \item Visible to opponent:
\begin{enumerate}
    \item Size, influenced by time entered maturity
\end{enumerate}
    \item invisible to opponent:
\begin{enumerate}
    \item Energy level, influenced by size and past actions
    \item Abandon Rate, influences RR abandonment rate
    \item Aggressiveness, influences escalation in contests
    \item Encounter Rate, influences chance of being selected for an event
\end{enumerate}
\end{enumerate}
